Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-29 prop_letter.tex
prop_letter.tex Introduction Updating...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
In this paper, we model the quantum finite precision by quantum interval-valued
probability measures (IVPMs). Under this framework,

Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
However, it is not evident at all that this resource-aware perspective
does not alter the very foundations of quantum mechanics. In order
to analyze the quantum world with finite resource, we extend the classical
interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
and introduce a new framework: quantum IVPM...\newpage{}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Even if quantum mechanics is invented for more than 60 years, mysterious
quantum measurement is still a source of different interpretations
and non-classical phenomena, including non-locality and contextuality~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
In contrast to the idealized measurement process, an actual experiment
is bounded by resources and must be finite precision. Whether finite
precision measurement in reality affect the idealized quantum concept,
e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
and the very foundation of quantum mechanics is still a problem. In
this letter, we model the finite precision quantum measurement by
quantum interval-valued probability measures (IVPMs) which provides
not only a uniform framework to understand Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
but also some examples which cannot be explained by the Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.

Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
The tension between finite precision measurement and the foundation
of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
and Kent~\cite{Kent1999} proved the original definition of contextuality
based on infinitely precised complex numbers cannot be experimental
verified. There were a long debate about whether contextuality could
be experimental verified or not~\cite{Mermin1999,Peres2003,BarrettKent2004}.

In order to analyze the quantum world with finite resource, we extend
the classical interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
and introduce a new framework: quantum IVPM...\newpage{}
